---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
# Tree GenViz

Todo

- variable branch peice length [✓]
- Make work with data instead of Gen []
- Save direction as variable [✓]

# Packages

```{r}
library(tidyverse)
library(ehlib)
```

# Loading custom functions

```{r}
sapply(paste0("R/", list.files("R/")), source, .GlobalEnv)
```

Function for random variable angle, variable branch length, and variable twig twig length. 

```{r}
angle_fun <- function(n, min_angle = 10, max_angle = 20) {
  sign <- sample(c(-1, 1), size = n, replace = TRUE) / 360 * 2 * pi
  size <- sample(min_angle:max_angle, size = n, replace = TRUE)
  sign * size
}

length_fun <- function(n) rpois(n = n, lambda = 20)

twig_fun <- function(n) ehlib::rztpois(n = n, lambda = 2)
```

## Example

```{r}
treeViz(5, angle_fun, length_fun)
```

### Single branch

Minimal branch.

```{r}
treeViz(1, angle_fun, length_fun) %>%
  ggplot(aes(x = x_from, xend = x_to,
             y = y_from, yend = y_to, 
             group = group)) +
  geom_curve(curvature = 0) +
  coord_fixed() +
  theme_void()
```

With colors depending on direction of path.

```{r}
treeViz(1, angle_fun, length_fun) %>%
  mutate(turn_col = angle > 0) %>%
  ggplot(aes(x = x_from, xend = x_to,
             y = y_from, yend = y_to, 
             group = group, color = turn_col)) +
  geom_curve(curvature = 0) +
  coord_fixed() +
  theme_void() +
  guides(color = "none")
```

### Whole tree

Minimal tree. Color by branch id.

```{r}
treeViz(25, angle_fun, length_fun) %>%
  ggplot(aes(x = x_from, xend = x_to,
             y = y_from, yend = y_to, 
             group = group, color = group)) +
  geom_curve(curvature = 0, alpha = 0.4) +
  coord_fixed() +
  theme_void() +
  guides(color = "none")
```

Tree. Color depending of direction.

```{r}
treeViz(100, angle_fun, length_fun) %>%
    mutate(turn_col = angle > 0) %>%
  ggplot(aes(x = x_from, xend = x_to,
             y = y_from, yend = y_to, 
             group = group, color = turn_col)) +
  geom_curve(curvature = 0, alpha = 0.3) +
  coord_fixed() +
  theme_void() +
  guides(color = "none") +
  scale_color_manual(values = c("#A3BE8C", "#BF616A"))
```

Variable twig length.

```{r}
angle_fun <- function(n, min_angle = 20, max_angle = 40) {
  sign <- sample(c(-1, 1), size = n, replace = TRUE) / 360 * 2 * pi
  size <- sample(min_angle:max_angle, size = n, replace = TRUE)
  sign * size
}
length_fun <- function(n) rpois(n = n, lambda = 20)

twig_fun <- function(n) ehlib::rztpois(n = n, lambda = 1)

treeViz(50, angle_fun, length_fun, twig_fun) %>%
  ggplot(aes(x = x_from, xend = x_to,
             y = y_from, yend = y_to, 
             group = group, color = group)) +
  geom_curve(curvature = 0, alpha = 0.4) +
  coord_fixed() +
  theme_void() +
  guides(color = "none")
```

